### 2022-11-03 paper.Rmd
Plots updated

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")

@@

library(gtExtras)
library(papaja)
library(papaja)
library(lordif)
library(tabledown)
papaja::r_refs("references.bib")
renv::snapshot()

@@

@@

```{r ggiteminfo, include=F}
library(tabledown)
observe_list = list()
for (i in 1:ncol(observe.refit)) {
  p = ggiteminfo(observe.fit.2, i,6)+ggtitle(i)
  observe_list[[i]] = p
}

describe_list = list()
for (i in 1:ncol(describe.refit)) {
  p = ggiteminfo(describe.fit.2, i,6)+ggtitle(i)
  describe_list[[i]] = p
}

awareness_list = list()
for (i in 1:ncol(awareness.refit)) {
  p = ggiteminfo(awareness.fit.2, i,6)+ggtitle(i)
  awareness_list[[i]] = p
}

nonjudge_list = list()
for (i in 1:ncol(nonjudge.refit)) {
  p = ggiteminfo(nonjudge.fit.2, i,6)+ggtitle(i)
  nonjudge_list[[i]] = p
}

nonreact_list = list()
for (i in 1:ncol(nonreact.refit)) {
  p = ggiteminfo(nonreact.fit.2, i,6)+ggtitle(i)
  nonreact_list[[i]] = p
}

@@

```{r plot-saveloop, eval=FALSE, include=FALSE}
for (i in 1:ncol(observe.refit)) {

  temp_plot = ggiteminfo(observe.fit.2, i,6)

  ggsave(temp_plot, file=paste0("Figures/OBSERVE_", i,".png"), width = 14, height = 10, units = "cm")
}

@@

```{r fig-occ, fig.cap= "Option Charecteristics curve (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
cowplot::plot_grid(observe.OCC, describe.OCC, awareness.OCC, nonjudge.OCC, nonreact.OCC, labels = "AUTO",ncol=2, label_size = 8,align = "v")
```

>>>>

```{r setup-chunk, include=FALSE}
#This chunk sets the global chunk environment.

knitr::opts_chunk$set(dev = "png",
                      dpi = 600,
                      echo = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning=F)
set.seed(2023)
par(family = "Arial")
# options(knitr.duplicate.label = "allow")

@@

library(gtExtras)
library(papaja)
library(papaja)
library(lordif)
library(tabledown)
library(ggsci)
papaja::r_refs("references.bib")
# renv::snapshot()

@@

```{r apatheme, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        plot.title = element_text(size = 8),
        legend.text = element_text(size = 8),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r ggitem-info-all-plots}
#We used all item-info plot in the manuscript
#Observe
info.item1 <- ggiteminfo(observe.fit.2,1,6)+ggtitle("Obs:item01")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+ geom_area(fill =  "#E64B3599")

info.item6 <- ggiteminfo(observe.fit.2,2,6)+ggtitle("Obs:item06")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item11 <- ggiteminfo(observe.fit.2,3,6)+ggtitle("Obs:item11")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item15 <- ggiteminfo(observe.fit.2,4,6)+ggtitle("Obs:item15")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item20 <- ggiteminfo(observe.fit.2,5,6)+ggtitle("Obs:item20")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item26 <- ggiteminfo(observe.fit.2,6,6)+ggtitle("Obs:item26")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item31 <- ggiteminfo(observe.fit.2,7,6)+ggtitle("Obs:item31")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

info.item36 <- ggiteminfo(observe.fit.2,8,6)+ggtitle("Obs:item36")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#E64B3599")

observe_iic <- cowplot::plot_grid(
 info.item1, info.item6,info.item11,info.item15, info.item20,info.item26, info.item31, info.item36,
                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 25,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/observe_info.png",observe_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

# Describe

info.item7 <- ggiteminfo(describe.fit.2,1,6)+ggtitle("Des:item07")+apatheme+scale_y_continuous(breaks=c(0,.8,1.5), limits = c(0, 1.5))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill="#4DBBD599")

info.item22 <- ggiteminfo(describe.fit.2,2,6)+ggtitle("Des:item22")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill=  "#4DBBD599")

info.item27 <- ggiteminfo(describe.fit.2,3,6)+ggtitle("Des:item27")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#4DBBD599")

info.item32 <- ggiteminfo(describe.fit.2,4,6)+ggtitle("Des:item32")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.8,1.5), limits = c(0, 1.5))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#4DBBD599")

info.item37 <- ggiteminfo(describe.fit.2,5,6)+ggtitle("Des:item37")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#4DBBD599")

describe_iic <- cowplot::plot_grid(

 info.item7, info.item22, info.item27, info.item32, info.item37,

                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/describe_info.png",describe_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

#Actwar
info.item5 <- ggiteminfo(awareness.fit.2,1,6)+ggtitle("Actw:item05")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item8 <- ggiteminfo(awareness.fit.2,2,6)+ggtitle("Actw:item08")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item13 <- ggiteminfo(awareness.fit.2,3,6)+ggtitle("Actw:item13")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item18 <- ggiteminfo(awareness.fit.2,4,6)+ggtitle("Actw:item18")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item23 <- ggiteminfo(awareness.fit.2,5,6)+ggtitle("Actw:item23")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item28 <- ggiteminfo(awareness.fit.2,6,6)+ggtitle("Actw:item28")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item34 <- ggiteminfo(awareness.fit.2,7,6)+ggtitle("Actw:item34")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.8,1.5), limits = c(0, 1.5))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item38 <- ggiteminfo(awareness.fit.2,8,6)+ggtitle("Actw:item38")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

actwar_icc <- cowplot::plot_grid(

 info.item5,info.item8, info.item13, info.item18, info.item23, info.item28, info.item34, info.item38,
                    labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/actwar_info.png",actwar_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

#Nonjudge

info.item3 <- ggiteminfo(nonjudge.fit.2,1,6)+ggtitle("Nonj:item03")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item10 <- ggiteminfo(nonjudge.fit.2,2,6)+ggtitle("Nonj:item10")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item17 <- ggiteminfo(nonjudge.fit.2,3,6)+ggtitle("Nonj:item17")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item25 <- ggiteminfo(nonjudge.fit.2,4,6)+ggtitle("Nonj:item25")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item30 <- ggiteminfo(nonjudge.fit.2,5,6)+ggtitle("Nonj:item30")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item35 <- ggiteminfo(nonjudge.fit.2,6,6)+ggtitle("Nonj:item35")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item39 <- ggiteminfo(nonjudge.fit.2,7,6)+ggtitle("Nonj:item39")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

nonjudge_icc <- cowplot::plot_grid(

 info.item3, info.item10, info.item17, info.item25, info.item30, info.item35, info.item39,
                   labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")
# ggsave("Figures/nonjudge_info.png",nonjudge_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

#nonreact

info.item4 <- ggiteminfo(nonreact.fit.2,1,6)+ggtitle("Nonr:item04")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

info.item9 <- ggiteminfo(nonreact.fit.2,2,6)+ggtitle("Nonr:item09")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

info.item19 <- ggiteminfo(nonreact.fit.2,3,6)+ggtitle("Nonr:item19")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

info.item21 <- ggiteminfo(nonreact.fit.2,4,6)+ggtitle("Nonr:item21")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

info.item24 <- ggiteminfo(nonreact.fit.2,5,6)+ggtitle("Nonr:item24")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")
info.item29 <- ggiteminfo(nonreact.fit.2,6,6)+ggtitle("Nonr:item29")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

info.item33 <- ggiteminfo(nonreact.fit.2,7,6)+ggtitle("Nonr:item33")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#B09C8599")

nonreact_icc <- cowplot::plot_grid(

 info.item4, info.item9, info.item19, info.item21, info.item24, info.item29, info.item33,
                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/nonreact.png",nonreact_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

all_info <- cowplot::plot_grid(
 info.item1, info.item6,info.item11,info.item15, info.item20,info.item26, info.item31, info.item26,
 info.item7, info.item22, info.item27, info.item32, info.item37,
 info.item5,info.item8, info.item13, info.item18, info.item23, info.item28, info.item34, info.item38,
 info.item3, info.item10, info.item17, info.item25, info.item30, info.item35, info.item39,
 info.item4, info.item9, info.item19, info.item21, info.item24, info.item29, info.item33,
                               labels = NULL,
                               align="v",
                               ncol = 6,
                               label_size = 18,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

ggsave("Figures/Fig3.png",all_info , units = "mm", width = 174, height = 234, dpi = 600, bg = "white")

@@

```{r problematic-icc, include=F}
#Publication quality OCC
library(ggsci)

#For legends
item01.icc.legends <- ggicc(observe.fit.2,1,6)+ggtitle("Observe: item01")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

# 38, 22, 39, 3, and 17

item38.icc <- tabledown::ggicc(awareness.fit.2,8,6)+ggtitle("item38")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

item22.icc <- ggicc(describe.fit.2,2,6)+ggtitle("item22")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

item39.icc <- ggicc(nonjudge.fit.2,7,6)+ggtitle("item39")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

item03.icc <- ggicc(nonjudge.fit.2,1,6)+ggtitle("item03")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

item17.icc <- ggicc(nonjudge.fit.2,3,6)+ggtitle("item17")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

item26.icc <- ggicc(observe.fit.2,6,6)+ggtitle("Representative OCC: item26")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.legends <- ggicc(observe.fit.2,1,6)+ggtitle("Observe: item01")+apatheme+scale_color_npg()+ theme(legend.position = "bottom")
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
icc.legend <- cowplot::get_legend(icc.legends)

problematic_icc <- cowplot::plot_grid(
  item26.icc,item38.icc,item22.icc,item39.icc,item03.icc,item17.icc,
                               labels = "AUTO",
                               align="v",
                               ncol = 3,
                               label_size = 15,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

problematic_icc_2 <- plot_grid(problematic_icc, icc.legend, ncol = 1, rel_heights =  c(1, .12))

ggsave("Figures/Fig4.png",problematic_icc_2 , units = "mm", width = 174, height = 117, dpi = 600, bg = "white")

```{r icc-all-plots}
#We have included this as a supplementary
#Observe
icc.item1 <- ggicc(observe.fit.2,1,6)+ggtitle("item01")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item6 <- ggicc(observe.fit.2,2,6)+ggtitle("item06")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item11 <- ggicc(observe.fit.2,3,6)+ggtitle("item11")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item15 <- ggicc(observe.fit.2,4,6)+ggtitle("item15")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item20 <- ggicc(observe.fit.2,5,6)+ggtitle("item20")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item26 <- ggicc(observe.fit.2,6,6)+ggtitle("item26")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item31 <- ggicc(observe.fit.2,7,6)+ggtitle("item31")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item36 <- ggicc(observe.fit.2,8,6)+ggtitle("item26")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

observe_icc <- cowplot::plot_grid(
 icc.item1, icc.item6,icc.item11,icc.item15, icc.item20,icc.item26, icc.item31, icc.item36,
                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 25,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/observe_icc.png",observe_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

# Describe

icc.item7 <- ggicc(describe.fit.2,1,6)+ggtitle("item07")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item22 <- ggicc(describe.fit.2,2,6)+ggtitle("item22")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item27 <- ggicc(describe.fit.2,3,6)+ggtitle("item27")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item32 <- ggicc(describe.fit.2,4,6)+ggtitle("item32")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item37 <- ggicc(describe.fit.2,5,6)+ggtitle("item37")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

describe_icc <- cowplot::plot_grid(

 icc.item7, icc.item22, icc.item27, icc.item32, icc.item37,

                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/describe_icc.png",describe_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

observe_describe <- cowplot::plot_grid(

observe_icc, describe_icc,   labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/observe_describe.png",observe_describe , units = "mm", width = 174, height = 117, dpi = 300, bg = "white")

#Actwar
icc.item5 <- ggicc(awareness.fit.2,1,6)+ggtitle("item05")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item8 <- ggicc(awareness.fit.2,2,6)+ggtitle("item08")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item13 <- ggicc(awareness.fit.2,3,6)+ggtitle("item13")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item18 <- ggicc(awareness.fit.2,4,6)+ggtitle("item18")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item23 <- ggicc(awareness.fit.2,5,6)+ggtitle("item23")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item28 <- ggicc(awareness.fit.2,6,6)+ggtitle("item28")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item34 <- ggicc(awareness.fit.2,7,6)+ggtitle("item34")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item38 <- ggicc(awareness.fit.2,8,6)+ggtitle("item38")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

actwar_icc <- cowplot::plot_grid(

 icc.item5,icc.item8, icc.item13, icc.item18, icc.item23, icc.item28, icc.item34, icc.item38,
                    labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/actwar_icc.png",actwar_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

#Nonjudge

icc.item3 <- ggicc(nonjudge.fit.2,1,6)+ggtitle("item03")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item10 <- ggicc(nonjudge.fit.2,2,6)+ggtitle("item10")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item17 <- ggicc(nonjudge.fit.2,3,6)+ggtitle("item17")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item25 <- ggicc(nonjudge.fit.2,4,6)+ggtitle("item25")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item30 <- ggicc(nonjudge.fit.2,5,6)+ggtitle("item30")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item35 <- ggicc(nonjudge.fit.2,6,6)+ggtitle("item35")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item39 <- ggicc(nonjudge.fit.2,7,6)+ggtitle("item39")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

nonjudge_icc <- cowplot::plot_grid(

 icc.item3, icc.item10, icc.item17, icc.item25, icc.item30, icc.item35, icc.item39,
                   labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")
# ggsave("Figures/nonjudge_icc.png",nonjudge_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

#nonreact

icc.item4 <- ggicc(nonreact.fit.2,1,6)+ggtitle("item04")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item9 <- ggicc(nonreact.fit.2,2,6)+ggtitle("item09")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item19 <- ggicc(nonreact.fit.2,3,6)+ggtitle("item19")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item21 <- ggicc(nonreact.fit.2,4,6)+ggtitle("item21")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item24 <- ggicc(nonreact.fit.2,5,6)+ggtitle("item24")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item29 <- ggicc(nonreact.fit.2,6,6)+ggtitle("item29")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

icc.item33 <- ggicc(nonreact.fit.2,7,6)+ggtitle("item33")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

nonreact_icc <- cowplot::plot_grid(

 icc.item4, icc.item9, icc.item19, icc.item21, icc.item24, icc.item29, icc.item33,
                               labels = NULL,
                               align="v",
                               ncol = 2,
                               label_size = 20,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

# ggsave("Figures/nonreact.png",nonreact_icc , units = "mm", width = 84, height = 117, dpi = 300, bg = "white")

all_icc <- cowplot::plot_grid(
 icc.item1, icc.item6,icc.item11,icc.item15, icc.item20,icc.item26, icc.item31, icc.item26,
 icc.item7, icc.item22, icc.item27, icc.item32, icc.item37,
 icc.item5,icc.item8, icc.item13, icc.item18, icc.item23, icc.item28, icc.item34, icc.item38,
 icc.item3, icc.item10, icc.item17, icc.item25, icc.item30, icc.item35, icc.item39,
 icc.item4, icc.item9, icc.item19, icc.item21, icc.item24, icc.item29, icc.item33,
                               labels = "AUTO",
                               align="v",
                               ncol = 6,
                               label_size = 15,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

icc.legends <- ggicc(observe.fit.2,1,6)+ggtitle("Observe: item01")+apatheme+scale_color_npg()+ theme(legend.position = "bottom")
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
icc.legend <- cowplot::get_legend(icc.legends)

all_icc_2 <- plot_grid(all_icc, icc.legend, ncol = 1, rel_heights   = c(1, .12))

# ggsave("Figures/all_icc.png",all_icc_2 , units = "mm", width = 174, height = 234, dpi = 300, bg = "white")

@@

```{r fig-occ, fig.cap= "Option Charecteristics curve (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
knitr::include_graphics('Figures/Fig6.png', dpi =600)
